Q. Where and how do I get the Allegro library itself to install?\newline
A. You dont need to install Allegro, it comes with the planet package.

Q. I get errors about the planet download not completing.\newline
A. Planet sometimes has problems with very large packages, like this one.
You can always download the latest package from my home page and install it
on the command line.

http://www.rafkind.com/jon/showproject.php?id=27

To install on the command line type the following\newline
{\tt \$ planet -f allegro.plt kazzmir 1 4}

Those last two parameters can really be whatever you want, they are just
version numbers, but they should probably match the version that you
downloaded.

Q. The planet package wont install. I am on Ubuntu.\newline
A. Ubuntu is a binary distribution which doesnt come with the tools necessary
to build Allegro from source. To get these tools goto the ubuntu package
manager and install the following packages:

  {\tt make}\newline
  {\tt libx11-dev}

Planet wont know if Allegro doesn't build correctly so you will need to
uninstall the package before trying to install it again. This can be
accomplished like so:\newline
{\tt \$ planet -r kazzmir allegro.plt 1 4}

Replace the last two parameters with the version of Allegro you are trying to
use.

Q. I get an error like "Scheme->C: expects argument of type <int32>; given 50.3".\newline
A. This means you passed in a floating point number to an allegro function that requires an integer. You can use the \link{round*} method to convert a float to an integer or use the following code:

\begin{schemedisplay}
(define (my-round i)
  (inexact->exact (round i)))
\end{schemedisplay}

Q. How do I build stand-alone executable that use Allegro?\newline
A. The easiest way is to use 'create executable' from DrScheme\newline

Use the 'module' language from within DrScheme. Make sure your program is wrapped with a (module ...) s-expr.

\begin{schemedisplay}
(module mygame mzscheme
 ...
)
\end{schemedisplay}

Then click scheme->create executable and follow the options from there.
